---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  font-family: 'Indie Flower', cursive;
}

h1 {
  padding-bottom: 10px;
}

h2 {
  border: 2px solid #3498db
}
```

## Observational Study: Personalized Ad Patterns 


**Aim**
The aim of this  report explores the **` r nrow(latest_data)` ads** observed over personalised data. The occurrance and the certain trends that occur for personlized advertisements across various social media platforms. The variables tracked are include:
- **Duration**: Seconds before an ad could be skipped (or total time spent).  
- **Platform**: Social media platforms (e.g., Facebook, YouTube).  
- **Category**: Product/service type (e.g., Health & Fitness, Technology).  
The key components we are looking to explore include:
**KEY COMPONENTS:**
1. What platforms show the highest number of ads?
2. Which ad categories are most prevalent in personalized advertisements?
3. How long do users engage with ads before skipping them? 


## The Process of Data Collection:
- **Source** Ads that were observed over various social media platforms 
- **Observation** The data was logged after engaging with a personalized advertisement
- **Methods** The method used to extract data was Google Form, Rstudio and Dynamic RMarkdown Report 





```{r}
csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR4Ob7R_pvS4Bu--tfyHxVTpaMtxup_UElzzUTWVkZYo8ss2fSygodhA-_BZNi9kYDo7-181mFHPRql/pub?gid=1933024189&single=true&output=csv"
logged_data <- read_csv(csv_url)

#Renaming the variables of the data frame logged data using the rename()
# Rename variables by column position (like the screenshot example)
latest_data <- logged_data %>%
  rename(
    duration = 2,              
    platform = 3,              
    category = 4,              
    targeting_reason = 5,      
    details = 6                
  )

```


```{r}
num_ads <- latest_data$duration %>%
  length()

mean_duration <- latest_data$duration %>%
  mean(na.rm = TRUE) %>%
  round(2)

paste0("From a total of ", num_ads, " logged ads, the average duration of ad engagement before skipping was ", mean_duration, " seconds.")

```


```{r}
summary_stats <- latest_data %>%
  summarise(
    min_duration = min(duration, na.rm = TRUE),  
    mean_duration = mean(duration, na.rm = TRUE),  
    max_duration = max(duration, na.rm = TRUE),     
    total_obs = n()
  )

paste0(
  "From the dataset, there were ", summary_stats$total_obs, " ads logged. ",
  "The shortest ad duration was ", summary_stats$min_duration, " seconds, ",
  "the average duration was ", round(summary_stats$mean_duration, 2), " seconds, ",
  "and the longest ad duration was ", summary_stats$max_duration, " seconds."
)

```




```{r fig.width = 13, fig.height = 4}


category_plot <- latest_data %>%
  ggplot() +  
  geom_bar(aes(x = category, fill = category)) +
  labs(title = "Distribution for Ads by Category",
    subtitle = "Frequency of logged ad types (where multiple selections allowed)",
    caption = "Source: Observational Ad Logging",
    x = "Advertisement Category",
    y = "Total count")

print(category_plot)
```

```{r fig.width = 13, fig.height = 4}
platform_plot <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = platform, fill = platform)) +
  labs(title = "Distribution of Ads by Platform",
    subtitle = "Frequency of observed Advertisements across Social Media platforms",
    caption = "Source: Observational Ad Logging",
    x = "Platform",
    y = "Total number of Ads")


print(platform_plot)
```



